Computational Luminance Constancy from Naturalistic Images

### 2018-09-17 Revision1/Revision1.tex
final edits

\documentclass{jov}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{comment}

@@

We define the computational problem of luminance constancy as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic. This condition does not apply to our work - we consider full spectral variation in the stimuli. We chose the term luminance constancy to denote the generalization from achromatic stimuli. At the same time, we acknowledge that we are not studying the full problem of color constancy. Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.}.
The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
Obtaining the LRF from a known surface reflectance function requires two steps.
First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
Second, one normalizes the result by the luminance of the reference illuminant itself.
Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
Sometimes LRFs are expressed as a percentage.
Here we express LRFs as proportions, so that they take on values between 0.0 and 1.0. 
An LRF of 0.0 means that none of the light from the reference illuminant is reflected from the surface. 
An LRF of 1.0 means that all of the light from the reference illuminant is reflected from the surface.

@@

We used the Library base scene and a spherical target object.
The Library base scene contains 2 area lights. 
We inserted one additional spherical light source into the scene.
In condition 2 and 3, the overall intensity of the three light source illumination spectra were equal, while their relative shape varied.
The overall intensity varied from scene to scene.
The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
scenes. The geometry is shown in Figure~\ref{fig:3DScene} below.
Surface and illuminant spectra were sampled according to statistical models of naturally occurring spectra.
Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.

@@

We focused our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
In primary visual cortex, foveal receptive fields have a maximum spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}. 
We sought to understand how well responses from AMA-learned receptive fields at a similar scale could be used to achieve luminance constancy.

@@

In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRF.
Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
We chose this cost function because the estimates it yields at the boundaries of the LRF range are less biased than those obtained with the mean squared error cost function.

@@

Our rendering software allows us to compare the effect of background surface reflectances on target object LRF with and without simulation of secondary reflections of light from one object onto another. 
These secondary reflections were included in the dataset from which we report our primary results. 
When we turn off this feature of the rendering, we find (data not shown) that LRF estimation performance is essentially unchanged. 
Estimates with and without secondary reflections are very similar. 
This result suggests that the primary source of the estimation error in Condition 3 is caused by image-to-image variation in the reflectance of the background objects.

@@

To increase the representativeness of our rendered images, we used datasets of natural surface reflectance spectra and natural daylight illumination spectra. Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved. For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses. Some of these datasets focused on the reflectance of objects (e.g. fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}). Another issue, not addressed by these datasets, is relative frequency of different surface reflectivities in natural viewing. \citeNP{attewell2007distribution} performed a systematic survey, and report the distribution of an LRF-like quantity in natural scenes. Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.

@@

We studied the information available for LRF estimation using a 1°x1° image patch. As noted above this choice of size was motivated in part to use a spatial scale roughly commensurate with the scale of information integration in early visual cortex. Our general methods could be extended to study larger regions, and doing so would quantify the value of spatially remote information for luminance constancy.

>>>>

\documentclass{jov}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{gensymb}

@@

We define the computational problem of luminance constancy\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic. This condition does not apply to our work - we consider full spectral variation in the stimuli. We chose the term luminance constancy to denote the generalization from achromatic stimuli. At the same time we acknowledge that we are not studying the full problem of color constancy. Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.} as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function.
The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
Obtaining the LRF from a known surface reflectance function requires two steps.
First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
Second, one normalizes the result by the luminance of the reference illuminant itself.
Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
Sometimes LRFs are expressed as a percentage.
Here we express LRFs as proportions, so that they take on values between 0 and 1. 
An LRF of 0 means that none of the light from the reference illuminant is reflected from the surface. 
An LRF of 1 means that the luminance of the surface reflectance under the reference illuminant is the same as the luminance of a perfect reflector under that same illuminant.

@@

We used the Library base scene and a spherical target object.
The Library base scene contains 2 area lights. 
We inserted one additional spherical light source into the scene.
In Conditions 2 and 3, the overall intensities of the three light source illumination spectra were equal, while their relative shape varied. 
The overall intensity varied from scene to scene.
The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
scenes. The geometry is shown in Figure~\ref{fig:3DScene} below.
Surface and illuminant spectra were sampled according to statistical models of naturally occurring spectra.
Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.

@@

We focused our analysis on image regions local to the target by cropping the rendered images to $1\degree \times 1\degree$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
In primary visual cortex, foveal receptive fields have a maximum spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}. 
We sought to understand how well responses from AMA-learned receptive fields at a similar scale could be used to achieve luminance constancy.

@@

In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRF.
Training with both cost functions yielded similar estimation performance; the results reported here are for when the Kullback-Leibler divergence cost function was used in training.
We chose this cost function because the estimates it yields at the boundaries of the LRF range are less biased than those obtained with the mean squared error cost function.

@@

Our rendering software allows us to compare the effect of background surface reflectances on target object LRF with and without simulation of secondary reflections of light from one object onto another. 
These secondary reflections were included in the dataset from which we report our primary results. 
When we turn off this feature of the rendering, we find (data not shown) that LRF estimation performance is essentially unchanged. 
Estimates with and without secondary reflections are very similar. 
This result suggests that the primary source of the estimation error in Condition 3 is caused by direct effects of image-to-image variation in the reflectance of the background objects on the AMA responses.

@@

To increase the representativeness of our rendered images, we used datasets of natural surface reflectance spectra and natural daylight illumination spectra. Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved. For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses. Some of these datasets focused on the reflectance of objects (e.g. fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}). Another issue, not addressed by these datasets, is relative frequency of different surface reflectances in natural viewing. \citeNP{attewell2007distribution} performed a systematic survey, and report the distribution of an LRF-like quantity in natural scenes. Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.

@@

We studied the information available for LRF estimation using a $1\degree \times 1 \degree$ image patch. As noted above this choice of size was motivated in part to use a spatial scale roughly commensurate with the scale of information integration in early visual cortex. Our general methods could be extended to study larger regions, and doing so would quantify the value of spatially remote information for luminance constancy.
